---
title: "Text Analysis and Sentiment Analysis"
date: "11/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Data Exploration
```{r}
#Importing R libraries 

library(tidyverse)
libraries <- c("tidyverse", "lubridate", "magrittr", "ggplotgui", "pROC", "dplyr", "ggplot2", "broom", "rpart", "C50", "ranger", "randomForest", "caret", "lift", "ROCR", "xgboost", "glmnet")
lapply(libraries,library, character.only=TRUE)
```

Importing dataset
```{r}
txtanalysis <- read.csv("~/Desktop/Data Mining /yelpRestaurantReviews_sample_s21b.csv", sep=";")
view(txtanalysis)
glimpse(txtanalysis)
dim(txtanalysis)

```

No of reviews by star-rating and relation of funny to cool
```{r}
txtanalysis %>% group_by(state) %>% tally() %>% view()
txtanalysis %>% group_by(starsReview) %>% count()
fun<-ggplot(txtanalysis, aes(x= funny, y=starsReview)) + geom_point()
print(fun)
funcol<-ggplot(txtanalysis, aes(x= funny, y=cool)) + geom_point()
print(funcol)
```

Num of reviews by star-rating and relation of cool & useful
```{r}
col<-ggplot(txtanalysis, aes(x= cool, y=starsReview)) + geom_point()
print(col)
coluse<-ggplot(txtanalysis, aes(x= cool, y=useful)) + geom_point()
print(coluse)
```
Relation of useful and funny
```{r}
use<-ggplot(txtanalysis, aes(x= useful, y=starsReview)) + geom_point()
print(use)
usefun<-ggplot(txtanalysis, aes(x= useful, y=funny)) + geom_point()
print(usefun)
```

Tokenize the text column 
```{r}
library(sparklyr)
library(tidytext)
library(SnowballC)
library(textstem)
tkntxt<- txtanalysis %>% select(review_id,starsReview,text)%>%unnest_tokens(word,text)
dim(tkntxt)
head(tkntxt)
# count the total occurances of different words, & sort by most frequent
tkntxt%>%count(word,sort = TRUE)%>%top_n(10)
tkntxt<-tkntxt%>%anti_join(stop_words)
head(tkntxt)
tkntxt%>%distinct(word) %>%dim()
```
Finding out rare words and Removing them
```{r}
rw<-tkntxt%>%count(word,sort = TRUE)%>%filter(n<10)
rw
remrw<-anti_join(tkntxt,rw)
# Removing the terms in word which are digits
remrw1<-remrw%>%filter(str_detect(word,"[0-9]")==FALSE)
tkntxt<-remrw1
tkntxt%>% distinct(word)%>%dim()
```
Words associated with different star ratings 
```{r}
#check words by star rating of reviews 
tkntxt%>%group_by(starsReview)%>%count(word,sort = TRUE)
# proportion of word occurence by star ratings 
ws <- tkntxt%>%group_by(starsReview)%>%count(word, sort = TRUE)
ws<- ws%>%group_by(starsReview)%>%mutate(prop=n/sum(n))
# checking the proportion of love among reviews with 1,2,...5 stars
ws%>%filter(word=='love')
# what are the most commonly used words by star rating 
ws%>%group_by(starsReview)%>%arrange(starsReview,desc(prop))%>%view()
  #top 20 
ws%>%group_by(starsReview)%>%arrange(starsReview,desc(prop))%>%filter(row_number()<=20)%>%view()
ws%>%group_by(starsReview)%>%arrange(starsReview, desc(prop))%>% filter(row_number()<=20)%>% ggplot(aes(word, prop))+geom_col()+coord_flip()+facet_wrap((~starsReview))

# Words associated with higher/lower stars in general? (Average)
xx<- ws %>% group_by(word) %>% summarise( totWS = sum(starsReview*prop))
xx%>%top_n(20)
xx%>%top_n(-20)
tkntxt_stem<-tkntxt%>%mutate(word_stem=SnowballC::wordStem(word))
view(tkntxt_stem)
```

Stemming and Lemmatization

```{r}

tkntxt_stem <- tkntxt %>% mutate(word_stem = SnowballC::wordStem(word))
tkntxt_lemm <- tkntxt %>% mutate(word_lemma = textstem::lemmatize_words(word))

#Term frequency
#tokenize, remove stopwords, and lemmatize
tkntxt<-tkntxt %>% mutate(word = textstem::lemmatize_words(word))
# filter out words with less than 3 characters more than 15 characters
tkntxt<-tkntxt %>% filter(str_length(word)<=3 | str_length(word)<=15)
tkntxt<- tkntxt %>% group_by(review_id, starsReview) %>% count(word)

#tokenize, remove stopwords and lemmatize 
totWords<-tkntxt%>%group_by(review_id)%>%count(word, sort = TRUE)%>%summarize(total=sum(n))
xx<-left_join(tkntxt,totWords)
view(xx)
xx<-xx%>%mutate(tf=n/total) # Error Working on it 
head(xx)
```
```{r}
#We can use the bind_tfidf function to calculate the tf, idf and tfidf values
tkntxt<-tkntxt %>% bind_tf_idf(word, review_id, n)
```

Sentiment Analysis
```{r}

library(textdata)

#Using dictionaries
get_sentiments("bing") %>% view()
get_sentiments("nrc") %>% view()
get_sentiments("afinn") %>% view()

#get sentiment of words in tkntxt – using join
rrSenti_bing<- tkntxt %>% left_join( get_sentiments("bing"), by="word")

#Retaining words which match the sentiment dictionary
rrSenti_bing<- tkntxt %>% inner_join( get_sentiments("bing"), by="word")

#counting occurrences of positive/negative sentiment words in the reviews
xx<-rrSenti_bing %>% group_by(word, sentiment) %>% summarise(totOcc=sum(n)) %>% arrange(sentiment, desc(totOcc))

#negating counts for the negative sentiment words
xx<- xx %>% mutate (totOcc=ifelse(sentiment=="positive", totOcc, -totOcc))

# Most positive and most negative words in reviews
xx<-ungroup(xx) 
xx %>% top_n(25)
xx %>% top_n(-25)

#Plotting the above
rbind(top_n(xx, 25), top_n(xx, -25)) %>% ggplot(aes(word, totOcc, fill=sentiment)) +geom_col()+coord_flip()
#or, with a better reordering of words
rbind(top_n(xx, 25), top_n(xx, -25)) %>% mutate(word=reorder(word,totOcc)) %>% ggplot(aes(word, totOcc, fill=sentiment))+geom_col()+coord_flip()

#Using "nrc" dictionary
rrSenti_nrc<-tkntxt %>% inner_join(get_sentiments("nrc"), by="word") %>%
group_by (word, sentiment) %>% summarise(totOcc=sum(n)) %>%
arrange(sentiment, desc(totOcc))

#No of words for different sentiment categories
rrSenti_nrc %>% group_by(sentiment) %>% summarise(count=n(), sumn=sum(totOcc))

#top few words for different sentiments
rrSenti_nrc %>% group_by(sentiment) %>% arrange(sentiment, desc(totOcc))%>% top_n(10) %>% view()

#Suppose you want to consider {anger, disgust, fear sadness, negative} to denote 'bad' reviews,and {positive, joy, anticipation, trust} to denote 'good' reviews

xx<-rrSenti_nrc %>% mutate(goodBad=ifelse(sentiment %in% c('anger', 'disgust', 'fear', 'sadness', 'negative'), -totOcc, ifelse(sentiment %in% c('positive', 'joy', 'anticipation', 'trust'), totOcc, 0)))

xx<-ungroup(xx)
top_n(xx, -20)
top_n(xx, 20)

#plot graph

rbind(top_n(xx, 25), top_n(xx, -25)) %>% mutate(word=reorder(word,goodBad)) %>% ggplot(aes(word, goodBad, fill=goodBad)) +geom_col()+coord_flip()


```

Analysis by review sentiment

```{r}

#summarising positive/negative sentiment words per review
revSenti_bing <- rrSenti_bing %>% group_by(review_id, starsReview) %>%
summarise(nwords=n(),posSum=sum(sentiment=='positive'),
negSum=sum(sentiment=='negative'))

#calculating sentiment score based on proportion of positive, negative words
revSenti_bing<- revSenti_bing %>% mutate(posProp=posSum/nwords, negProp=negSum/nwords)
revSenti_bing<- revSenti_bing%>% mutate(sentiScore=posProp-negProp)

#do review star ratings correspond to the positive/negative sentiment words
revSenti_bing %>% group_by(starsReview) %>%
summarise(avgPos=mean(posProp), avgNeg=mean(negProp), avgSentiSc=mean(sentiScore))

#Using AFinn dictionary

rrSenti_afinn<- tkntxt %>% inner_join(get_sentiments("afinn"), by="word")

revSenti_afinn <- rrSenti_afinn %>% group_by(review_id, starsReview)%>% summarise(nwords=n(),sentiSum =sum(value))

revSenti_afinn %>% group_by(starsReview)%>% 
  summarise(avgLen=mean(nwords), avgSenti=mean(sentiSum))


```


```{r}
#considering reviews with 1 to 2 stars as negative, and this with 4 to 5 stars as positive
revSenti_afinn <- revSenti_afinn %>% mutate(hiLo = ifelse(starsReview <= 2, -1, ifelse(starsReview >=4, 1, 0 )))

revSenti_afinn <- revSenti_afinn %>% mutate(pred_hiLo=ifelse(sentiSum > 0, 1, -1))

#filter out the reviews with 3 stars, and get the confusion matrix for hiLo vs pred_hiLo
xx<-revSenti_afinn %>% filter(hiLo!=0)
table(actual=xx$hiLo, predicted=xx$pred_hiLo )

#considering reviews with 1 stars as negative, and this with 5 stars as positive
revSenti_afinn <- revSenti_afinn %>% mutate(hiLo=ifelse(starsReview<2,-1, ifelse(starsReview>4, 1, 0 )))
revSenti_afinn <- revSenti_afinn %>% mutate(pred_hiLo=ifelse(sentiSum >0, 1, -1))

xx<-revSenti_afinn %>% filter(hiLo!=0)
table(actual=xx$hiLo, predicted=xx$pred_hiLo )
```

Creating Models to Predict the Review Sentiment
```{r}

library(textdata)

#Using dictionaries
get_sentiments("bing") %>% view()
get_sentiments("nrc") %>% view()
get_sentiments("afinn") %>% view()

#get sentiment of words in tkntxt – using join
rrSenti_bing<- tkntxt %>% left_join( get_sentiments("bing"), by="word")

#to retain only the words which match the sentiment dictionary, do an inner-join
rrSenti_bing<- tkntxt %>% inner_join( get_sentiments("bing"), by="word")

#count the occurrences of positive/negative sentiment words in the reviews
xx<-rrSenti_bing %>% group_by(word, sentiment) %>% summarise(totOcc=sum(n)) %>% arrange(sentiment, desc(totOcc))

#negate the counts for the negative sentiment words
xx<- xx %>% mutate (totOcc=ifelse(sentiment=="positive", totOcc, -totOcc))

# which are the most positive and most negative words in reviews
xx<-ungroup(xx) # Important to ungroup (ie remove the grouping from earlier step)
xx %>% top_n(25)
xx %>% top_n(-25)

#You can plot these
rbind(top_n(xx, 25), top_n(xx, -25)) %>% ggplot(aes(word, totOcc, fill=sentiment)) +geom_col()+coord_flip()
#or, with a better reordering of words
rbind(top_n(xx, 25), top_n(xx, -25)) %>% mutate(word=reorder(word,totOcc)) %>% ggplot(aes(word, totOcc, fill=sentiment))+geom_col()+coord_flip()

#with "nrc" dictionary
rrSenti_nrc<-tkntxt %>% inner_join(get_sentiments("nrc"), by="word") %>%
group_by (word, sentiment) %>% summarise(totOcc=sum(n)) %>%
arrange(sentiment, desc(totOcc))

rrSenti_nrcleft<-tkntxt %>% left_join(get_sentiments("nrc"), by="word") %>%
group_by (word, sentiment) %>% summarise(totOcc=sum(n)) %>%
arrange(sentiment, desc(totOcc))

#How many words are there for the different sentiment categories
rrSenti_nrc %>% group_by(sentiment) %>% summarise(count=n(), sumn=sum(totOcc))

#top few words for different sentiments
rrSenti_nrc %>% group_by(sentiment) %>% arrange(sentiment, desc(totOcc))%>% top_n(10) %>% view()

#Suppose you want to consider {anger, disgust, fear sadness, negative} to denote 'bad' reviews,and {positive, joy, anticipation, trust} to denote 'good' reviews



###################Made Change in Next Line Changed "good&baad" to "goodbad" ################



xx<-rrSenti_nrc %>% mutate(goodBad=ifelse(sentiment %in% c('anger', 'disgust', 'fear', 'sadness', 'negative'), -totOcc, ifelse(sentiment %in% c('positive', 'joy', 'anticipation', 'trust'), totOcc, 0)))

xx<-ungroup(xx)
top_n(xx, -20)
top_n(xx, 20)

#plot graph

rbind(top_n(xx, 25), top_n(xx, -25)) %>% mutate(word=reorder(word,goodBad)) %>% ggplot(aes(word, goodBad, fill=goodBad)) +geom_col()+coord_flip()


```

Classificatin of stars as high/low based on aggregated sentiment of words in the reviews

```{r}
#considering reviews with 1 to 2 stars as negative, and this with 4 to 5 stars as positive
revSenti_afinn <- revSenti_afinn %>% mutate(hiLo = ifelse(starsReview <= 2, -1, ifelse(starsReview >=4, 1, 0 )))

revSenti_afinn <- revSenti_afinn %>% mutate(pred_hiLo=ifelse(sentiSum > 0, 1, -1))

#filter out the reviews with 3 stars, and get the confusion matrix for hiLo vs pred_hiLo
xx<-revSenti_afinn %>% filter(hiLo!=0)
table(actual=xx$hiLo, predicted=xx$pred_hiLo )

#considering reviews with 1 stars as negative, and this with 5 stars as positive
revSenti_afinn <- revSenti_afinn %>% mutate(hiLo=ifelse(starsReview<2,-1, ifelse(starsReview>4, 1, 0 )))
revSenti_afinn <- revSenti_afinn %>% mutate(pred_hiLo=ifelse(sentiSum >0, 1, -1))

xx<-revSenti_afinn %>% filter(hiLo!=0)
table(actual=xx$hiLo, predicted=xx$pred_hiLo )
##roc
#rocqc <- roc(revSenti_afinn$hiLo, revSenti_afinn[,2], levels=c(-1, 1))
```

Creating Models to predict the review sentiment
```{r}

#Bing
revDTM_sentiBing <- rrSenti_bing %>% pivot_wider( id_cols = review_id, names_from = word, values_from = tf_idf)
revDTM_sentiBing <- rrSenti_bing %>% pivot_wider(id_cols = c(review_id, starsReview), names_from = word, values_from = tf_idf) %>% ungroup()
dim(revDTM_sentiBing)
revDTM_sentiBing <- revDTM_sentiBing %>% filter(starsReview!=3) %>% mutate(hiLo=ifelse(starsReview<=2, -1, 1)) %>% select(-starsReview)
dim(revDTM_sentiBing)
revDTM_sentiBing %>% group_by(hiLo) %>% tally()
###### afinn
revDTM_sentiafinn <- rrSenti_afinn %>% pivot_wider( id_cols =review_id, names_from = word, values_from = value)
revDTM_sentiafinn <- rrSenti_afinn %>% pivot_wider(id_cols = c(review_id, starsReview), names_from = word, values_from = tf_idf) %>% ungroup()
dim(revDTM_sentiafinn)
revDTM_sentiafinn <- revDTM_sentiafinn %>% filter(starsReview!=3) %>% mutate(hiLo=ifelse(starsReview<=2, -1, 1)) %>% select(-starsReview)
dim(revDTM_sentiafinn)
revDTM_sentiafinn %>% group_by(hiLo) %>% tally()


#Random Forest
library(ranger)
#replace all the NAs with 0

#bing
revDTM_sentiBing <- revDTM_sentiBing %>% replace(., is.na(.), 0)
revDTM_sentiBing$hiLo <- as.factor(revDTM_sentiBing$hiLo)

### afinn
revDTM_sentiafinn <- revDTM_sentiafinn %>% replace(., is.na(.), 0)
revDTM_sentiafinn$hiLo <- as.factor(revDTM_sentiafinn$hiLo)

library(rsample)
#bing
revDTM_sentiBing_split<- initial_split(revDTM_sentiBing, 0.5)
revDTM_sentiBing_trn<- training(revDTM_sentiBing_split)
revDTM_sentiBing_tst<- testing(revDTM_sentiBing_split)

### afinn
revDTM_sentiafinn_split<- initial_split(revDTM_sentiafinn, 0.5)
revDTM_sentiafinn_trn<- training(revDTM_sentiafinn_split)
revDTM_sentiafinn_tst<- testing(revDTM_sentiafinn_split)

##Bing
rfModel1<-ranger(dependent.variable.name = "hiLo",data=revDTM_sentiBing_trn %>% select(-review_id), num.trees = 500,importance='permutation', probability = TRUE)
rfModel1
revSentiBing_predTrn<- predict(rfModel1, revDTM_sentiBing_trn %>% select(-review_id))$predictions
revSentiBing_predTst<- predict(rfModel1, revDTM_sentiBing_tst %>% select(-review_id))$predictions
table(actual=revDTM_sentiBing_trn$hiLo, preds=revSentiBing_predTrn[,2]>0.5)
table(actual=revDTM_sentiBing_tst$hiLo, preds=revSentiBing_predTst[,2]>0.5)
##### afinn
rfModel12<-ranger(dependent.variable.name = "hiLo",data=revDTM_sentiafinn_trn %>% select(-review_id), num.trees = 500,importance='permutation', probability = TRUE)
rfModel12
revSentiafinn_predTrn<- predict(rfModel12, revDTM_sentiafinn_trn %>% select(-review_id))$predictions
revSentiafinn_predTst<- predict(rfModel12, revDTM_sentiafinn_tst %>% select(-review_id))$predictions
table(actual=revDTM_sentiafinn_trn$hiLo, preds=revSentiafinn_predTrn[,2]>0.5)
table(actual=revDTM_sentiafinn_tst$hiLo, preds=revSentiafinn_predTst[,2]>0.5)
library(pROC)
#Bing
rocTrn <- roc(revDTM_sentiBing_trn$hiLo, revSentiBing_predTrn[,2], levels=c(-1, 1))
rocTst <- roc(revDTM_sentiBing_tst$hiLo, revSentiBing_predTst[,2], levels=c(-1, 1))
plot.roc(rocTrn, col='blue')
plot.roc(rocTst, col='red', add=TRUE)
legend("bottomright", legend=c("Training", "Test"),col=c("blue", "red"), lwd=2, cex=0.8, bty='n')
###### afinn
rocTrnafinn <- roc(revDTM_sentiafinn_trn$hiLo, revSentiafinn_predTrn[,2], levels=c(-1, 1))
rocTstafinn <- roc(revDTM_sentiafinn_tst$hiLo, revSentiafinn_predTst[,2], levels=c(-1, 1))
plot.roc(rocTrnafinn, col='blue')
plot.roc(rocTstafinn, col='red', add=TRUE)
legend("bottomright", legend=c("Training", "Test"),col=c("blue", "red"), lwd=2, cex=0.8, bty='n')

#Combined
rWords<-tkntxt %>% group_by(word)%>% summarise(nr=n()) %>% arrange(desc(nr))
top_n(rWords, 20)
top_n(rWords, -20)
reduced_rWords <- rWords %>% filter( nr < 6000 & nr > 30)
reduced_tkntxt <- left_join(reduced_rWords, tkntxt)
revDTM <- reduced_tkntxt %>% pivot_wider(id_cols = c(review_id,starsReview), names_from = word,values_from = tf_idf) %>% ungroup()
dim(revDTM)
revDTM <- revDTM %>% filter(starsReview!=3) %>% mutate(hiLo=ifelse(starsReview<=2, -1, 1)) %>% select(-starsReview)
revDTM<-revDTM %>% replace(., is.na(.), 0)
revDTM$hiLo<-as.factor(revDTM$hiLo)
revDTM_split<- initial_split(revDTM, 0.5)
revDTM_trn<- training(revDTM_split)
revDTM_tst<- testing(revDTM_split)
rfModel2<-ranger(dependent.variable.name = "hiLo", data=revDTM_trn %>%select(-review_id), num.trees = 500, importance='permutation', probability = TRUE)
rfModel2$variable.importance
revDTM_predTrn<- predict(rfModel2, revDTM_trn %>% select(-review_id))$predictions
revDTM_predTst<-predict(rfModel2, revDTM_tst %>% select(-review_id))$predictions
table(actual=revDTM_trn$hiLo, preds=revDTM_predTrn[,2]>0.5)
table(actual=revDTM_tst$hiLo, preds=revDTM_predTst[,2]>0.5)
roc_combTrn <- roc(revDTM_trn$hiLo, revDTM_predTrn[,2], levels=c(-1, 1))
roc_combTrn <- roc(revDTM_tst$hiLo, revDTM_predTst[,2], levels=c(-1, 1))
plot.roc(roc_comb, col='blue')
plot.roc(rocTst, col='red', add=TRUE)
legend("bottomright", legend=c("Training", "Test"),col=c("blue", "red"), lwd=2, cex=0.8, bty='n')
#SVM
library(e1071)
svmM1 <- svm(as.factor(hiLo) ~., data = revDTM_sentiBing_trn %>%select(-review_id),kernel="radial", cost=1, scale=FALSE) 
revDTM_predTrn_svm1<-predict(svmM1, revDTM_sentiBing_trn)
revDTM_predTst_svm1<-predict(svmM1, revDTM_sentiBing_tst)
table(actual= revDTM_sentiBing_trn$hiLo, predicted= revDTM_predTrn_svm1)
system.time( svmM2 <- svm(as.factor(hiLo) ~., data = revDTM_sentiBing_trn%>% select(-review_id), kernel="radial", cost=5, gamma=5, scale=FALSE) )
revDTM_predTrn_svm2<-predict(svmM2, revDTM_sentiBing_trn)
table(actual= revDTM_sentiBing_trn$hiLo, predicted= revDTM_predTrn_svm2)
revDTM_predTst_svm2<-predict(svmM2, revDTM_sentiBing_tst)
table(actual= revDTM_sentiBing_tst$hiLo, predicted= revDTM_predTst_svm2)
system.time( svm_tune <- tune(svm, as.factor(hiLo) ~., data = revDTM_sentiBing_trn %>% select(-review_id),kernel="radial", ranges = list( cost=c(0.1,1,10,50), gamma = c(0.5,1,2,5, 10)),scale=FALSE) )
svm_tune$performances
svm_tune$best.parameters
svm_tune$best.model
revDTM_predTrn_svm_Best<-predict(svm_tune$best.model, revDTM_sentiBing_trn)
table(actual= revDTM_sentiBing_trn$hiLo, predicted= revDTM_predTrn_svm_Best)
revDTM_predTst_svm_best<-predict(svm_tune$best.model, revDTM_sentiBing_tst)
table(actual= revDTM_sentiBing_tst$hiLo, predicted= revDTM_predTst_svm_best)

#NAIVE BAYES  
library(e1071)
nbModel1<-naiveBayes(hiLo ~ ., data=revDTM_sentiBing_trn %>% select(-review_id))
revSentiBing_NBpredTrn<-predict(nbModel1, revDTM_sentiBing_trn, type = "raw")
revSentiBing_NBpredTst<-predict(nbModel1, revDTM_sentiBing_tst, type = "raw")
table(actual= revDTM_sentiBing_trn$hiLo, predicted= revSentiBing_NBpredTrn[,2]>0.5)
table(actual= revDTM_sentiBing_tst$hiLo, predicted= revSentiBing_NBpredTst[,2]>0.5)
auc(as.numeric(revDTM_sentiBing_trn$hiLo), revSentiBing_NBpredTrn[,2])
auc(as.numeric(revDTM_sentiBing_tst$hiLo), revSentiBing_NBpredTst[,2])

##### afinn
nbModel12<-naiveBayes(hiLo ~ ., data=revDTM_sentiafinn_trn %>% select(-review_id))
revSentiafinn_NBpredTrn<-predict(nbModel12, revDTM_sentiafinn_trn, type = "raw")
revSentiafinn_NBpredTst<-predict(nbModel12, revDTM_sentiafinn_tst, type = "raw")
table(actual= revDTM_sentiafinn_trn$hiLo, predicted= revSentiafinn_NBpredTrn[,2]>0.5)
table(actual= revDTM_sentiafinn_tst$hiLo, predicted= revSentiafinn_NBpredTst[,2]>0.5)
auc(as.numeric(revDTM_sentiafinn_trn$hiLo), revSentiafinn_NBpredTrn[,2])
auc(as.numeric(revDTM_sentiafinn_tst$hiLo), revSentiafinn_NBpredTst[,2])
####
library(pROC)
rocTrn <- roc(revDTM_sentiBing_trn$hiLo, revSentiBing_NBpredTrn[,2], levels=c(-1, 1))
rocTst <- roc(revDTM_sentiBing_tst$hiLo, revSentiBing_NBpredTst[,2], levels=c(-1, 1))
plot.roc(rocTrn, col='blue', legacy.axes = TRUE)
plot.roc(rocTst, col='red', add=TRUE)
legend("bottomright", legend=c("Training", "Test"), col=c("blue", "red"), lwd=2, cex=0.8, bty='n')
##### afinn
rocTrnafinn <- roc(revDTM_sentiafinn_trn$hiLo, revSentiafinn_NBpredTrn[,2], levels=c(-1, 1))
rocTstafinn <- roc(revDTM_sentiafinn_tst$hiLo, revSentiafinn_NBpredTst[,2], levels=c(-1, 1))
plot.roc(rocTrnafinn, col='blue', legacy.axes = TRUE)
plot.roc(rocTstafinn, col='red', add=TRUE)
legend("bottomright", legend=c("Training", "Test"), col=c("blue", "red"), lwd=2, cex=0.8, bty='n')
```

Summary of attributes and Comparison of Models

```{r}

#Looking into attributes

x<- txtanalysis %>% select (review_id, attributes)
paste(x[1,2])
x2<-x %>% mutate (atts = str_split( attributes, '\\|')) %>% unnest(atts)
dim(x2)
x3<- x2 %>% cbind( str_split_fixed ( x2$atts, ":", 2) ) 
colnames(x3)[4]<- 'attName'
colnames(x3)[5]<- 'attValue'
x3<-x3 %>% select (-c (attributes ,atts))
x3<-x3 %>% filter(str_length(x3$attName) > 0)

x4<-x3 %>% pivot_wider(names_from = attName, values_from = attValue)

dim(x4)
glimpse(x4)

#Analyzing 'Ambience'

paste(x4[1,3])
x5<-x4 %>% mutate (amb = str_split(Ambience, ","))

dim(x4)
dim(x5)

typeof(x5$amb)
x5$amb[1]
x5$amb[1000]

extractAmbience<-function(q)
{  sub(":.*","", q[which(str_extract(q,"True") == "True")])
}

x6<-x5 %>% mutate (amb = lapply (amb,extractAmbience ) ) 
dim(x6)
x6$amb[1]
x6$amb[1000]

#Count of examples by different values for 'Ambience'

x6 %>% group_by(amb) %>% tally() %>% view()
avg_starreview <- txtanalysis %>% select(review_id, starsReview)

x6 %>% filter(str_detect (amb,'romantic')) %>% count()
x6 %>% filter(str_detect (amb,'casual')) %>% count()
x6 %>% filter(str_detect (amb,'classy')) %>% count()



x7 <- merge(x6,avg_starreview)
x7 %>% filter(str_detect (amb,'romantic')) %>% summarise(n(),AvgStar = mean(starsReview))
x7 %>% filter(str_detect (amb,'casual')) %>% summarise(n(),AvgStar = mean(starsReview))
x7 %>% filter(str_detect (amb,'classy')) %>% summarise(n(),AvgStar = mean(starsReview))





#Analyzing 'BusinessParking'

paste(x4[1,5])
x5 <- x4 %>% mutate( bsnsPrk = str_split( BusinessParking, ","))

dim(x4)
dim(x5)

typeof(x5$bsnsPrk)

x5$bsnsPrk[1]
x5$bsnsPrk[1000]

extractBuspark<-function(q) 
{  sub(":.*","", q[which(str_extract(q, "True") == "True")])
}

x6<-x5%>% mutate (bsnsPrk=lapply(bsnsPrk, extractBuspark ) ) 

#Count of examples by different values for 'Bus Park'

x6%>% group_by(bsnsPrk) %>% tally() %>% view()

x6%>% filter(str_detect (bsnsPrk,'lot'))%>% count()
x6%>% filter(str_detect (bsnsPrk,'street'))%>% count()
x6%>% filter(str_detect (bsnsPrk,'valet'))%>% count()
x6%>% filter(str_detect (bsnsPrk,'garage'))%>% count()


x7 <- merge(x6,avg_starreview)
x7%>% filter(str_detect (bsnsPrk,'lot'))%>% summarise(n(),AvgStar = mean(starsReview))
x7%>% filter(str_detect (bsnsPrk,'street'))%>% summarise(n(),AvgStar = mean(starsReview))
x7%>% filter(str_detect (bsnsPrk,'valet'))%>% summarise(n(),AvgStar = mean(starsReview))
x7%>% filter(str_detect (bsnsPrk,'garage'))%>% summarise(n(),AvgStar = mean(starsReview))


#Analyzing 'GoodForMeal'

paste(x4[1,7])
x5<-x4 %>% mutate (GdFrMl = str_split (GoodForMeal, ","))

dim(x4)
dim(x5)

typeof(x5$GdFrMl)

x5$GdFrMl[1]
x5$GdFrMl[1000]

extractgood4meal<-function(q) 
{  sub(":.*","", q[which(str_extract(q,"True") == "True")])
}

x6<-x5 %>% mutate (GdFrMl = lapply (GdFrMl, extractgood4meal ) ) 

#count of examples by different values for 'Good For Meal'

x6%>%group_by(GdFrMl) %>% tally() %>% view()

x6%>%filter(str_detect (GdFrMl,'latenight')) %>% count()
x6%>%filter(str_detect (GdFrMl,'lunch')) %>% count()
x6%>%filter(str_detect (GdFrMl,'dinner')) %>% count()



x7 <- merge(x6,avg_starreview)
x7%>%filter(str_detect (GdFrMl,'latenight')) %>% summarise(n(),AvgStar = mean(starsReview))
x7%>%filter(str_detect (GdFrMl,'lunch')) %>% summarise(n(),AvgStar = mean(starsReview))
x7%>%filter(str_detect (GdFrMl,'dinner')) %>% summarise(n(),AvgStar = mean(starsReview))



```





